Liveness-Based Garbage Collection for Lazy Languages

### 2016-02-15 paper/paper.tex
minor cleanups
minor rewrite

\documentclass[9pt,preprint,letter,nonatbib]{sigplanconf}
\usepackage{etex}
\usepackage{float}
\usepackage{mathrsfs}
%%\usepackage{lineno}
\usepackage{booktabs}
\usepackage{stmaryrd}
\usepackage{boxedminipage}
\usepackage[T1]{fontenc}
\usepackage{epsfig}
\usepackage{multirow}
\usepackage{url}
\usepackage[normalem]{ulem}
\usepackage{schemepgm}
\usepackage{graphicx}
\usepackage{graphpap}
\usepackage{tabularx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{pstricks}
\usepackage{pst-text}
\usepackage{pst-node}
\usepackage{pst-tree}
\usepackage{pst-rel-points}
\usepackage{bcprules}
\usepackage{subfigure}
\usepackage[boxed]{algorithm2e}
\usepackage{makecell}
\usepackage{balance}

@@

\section{Computing liveness and its encoding as DFA}\label{sec:computing}
%\section{Generating and storing liveness information}\label{sec:computing}
Section~\ref{sec:liveness}  gave   a  fully context-sensitive
liveness analysis which 
%$\mathcal{L}$ and $ref$ together
described the  liveness set for  each variable  in a function  body in
terms of  a symbolic demand  $\sigma$ and \Lfonly.  However,  we are yet
to describe  (i) how to obtain demand  transformers \Lfonly\ from
the  rule {\sc  live-define}, and  (ii)  how to  compute the  concrete
demand $\sigma$  on each function.   To do so,  we first need to  modify the
liveness rules to a different form.

@@

\vspace*{-6.5mm}
\section{The GC scheme}
\label{sec:GC-scheme}

@@

\appendix
%\section{Appendix: not to be included in the paper.}
%%%%% prasanna minefield
\begin{figure*}[b!]
\noindent{\Large \bf A. Minefield semantics (Not to be included in the paper) }
\begin{center}\footnotesize
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{|c|c|c|}
\hline
Premise & Transition & Rule name \\ 
\hline
\hline
&\makecell{ $\rho, (\rho', \ell, e, \cred{\sigma'})\!:\!S,
  \heap, \kappa, \cred{\sigma}$  $\rightsquigarrow \rho', S, \heap[\ell :=
    \kappa], e, \cred{\sigma'}$ }   &  {\sc const}
\\
\hline
& \makecell[t]{$\rho, (\rho', \ell, e, \cred{\sigma'})\!:\!S, \heap,
  (\CONS~x~y), \cred{\sigma}$  $\rightsquigarrow$ \\ $
  \rho', S, \heap[\ell := (\rho(x),\rho(y))], e, \cred{\sigma'}$}     &  {\sc cons} \\
\hline
\makecell[t]{ $\rho(x) \mbox{ is } \bot$} & $\rho, S,
  \heap, (\CAR~x), \cred{\sigma} \rightsquigarrow \bang$   &
{\sc car-bang} 
\\
\hline
\makecell[t]{$\heap(\rho(x)) \mbox{ is } (v, d)$} & \makecell[t]{$\rho, (\rho', \ell, e,
  \cred{\sigma'} )\!:\!S, \heap, (\CAR~x), \cred{\sigma}$  $
  \rightsquigarrow $ \\ $\rho', S, \heap[\ell := v], e, \cred{\sigma'}$}      &
{\sc car-select} \\
\hline
\makecell[t]{ $\heap(\rho(x))
\mbox{ is } \langle s, \rho'\rangle$ }& \makecell[t]{$\rho, S,
  \heap, (\CAR~x), \cred{\sigma} \rightsquigarrow $\\ $  \rho', (\rho, \rho(x),
  (\CAR~x), \cred{\sigma})\!:\!S, \heap, s, \cred{(\clazy \cup \acar)\sigma }$ }        &
{\sc car-clo}\\
\hline
\makecell[t]{$\heap(\rho(x)) \mbox{ is } (\langle s, \rho'\rangle, d)$} & \makecell[t]{$\rho,\, S,\,  \heap,\,
(\CAR~x), \cred{\sigma} \rightsquigarrow$ \\ $ \rho', \,(\rho, addr(\langle
s, \rho'\rangle), (\CAR~x),\cred{\sigma} )\!:\!S,\, \heap,\, s, \, \cred{\sigma}$ }     &
{\sc car-1-clo} \\
%% \hline

>>>>

\documentclass[9pt,preprint,nonatbib]{sigplanconf}
\usepackage{etex}
\usepackage{float}
\usepackage{mathrsfs}
%%\usepackage{lineno}
\usepackage{booktabs}
\usepackage{stmaryrd}
\usepackage{boxedminipage}
\usepackage[T1]{fontenc}
\usepackage{epsfig}
\usepackage{multirow}
\usepackage{url}
\usepackage[normalem]{ulem}
\usepackage{schemepgm}
\usepackage{graphicx}
\usepackage{graphpap}
\usepackage{tabularx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{pstricks}
\usepackage{pst-text}
\usepackage{pst-node}
\usepackage{pst-tree}
\usepackage{pst-rel-points}
\usepackage{bcprules}
\usepackage{subfigure}
\usepackage[boxed]{algorithm2e}
\usepackage{makecell}
\usepackage{balance}

@@

\section{Towards a  computable form of liveness}\label{sec:computing}
%\section{Generating and storing liveness information}\label{sec:computing}
The analysis in Section~\ref{sec:liveness} is fully context-sensitive, 
describing the  liveness sets  in a function body in
terms of a symbolic demand $\sigma$  and \Lfonly. However, we are yet to
describe (i) how to obtain demand transformers \Lfonly\ from the rule
{\sc live-define} , and (ii) how to compute the concrete demand $\sigma$ on
each function. To do so, we first need to modify the liveness rules
to a slightly different form.

@@

%\vspace*{-6.5mm}
\section{The GC scheme}
\label{sec:GC-scheme}

@@

\appendix
%\section{Appendix: not to be included in the paper.}
%%%%% prasanna minefield
\begin{figure*}[b!]
\noindent{\Large \bf A. Complete minefield semantics}
\begin{center}\footnotesize
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{|c|c|c|}
\hline
Premise & Transition & Rule name \\ 
\hline
\hline
&\makecell{ $\rho, (\rho', \ell, e, \cred{\sigma'})\!:\!S,
  \heap, \kappa, \cred{\sigma}$  $\rightsquigarrow \rho', S, \heap[\ell :=
    \kappa], e, \cred{\sigma'}$ }   &  {\sc const}
\\
\hline
& \makecell[t]{$\rho, (\rho', \ell, e, \cred{\sigma'})\!:\!S, \heap,
  (\CONS~x~y), \cred{\sigma}$  $\rightsquigarrow$ \\ $
  \rho', S, \heap[\ell := (\rho(x),\rho(y))], e, \cred{\sigma'}$}     &  {\sc cons} \\
\hline
\makecell[t]{ $\rho(x) \mbox{ is } \bot$} & $\rho, S,
  \heap, (\CAR~x), \cred{\sigma} \rightsquigarrow \bang$   &
{\sc car-bang} 
\\
\hline
\makecell[t]{$\heap(\rho(x)) \mbox{ is } (v, d)$} & \makecell[t]{$\rho, (\rho', \ell, e,
  \cred{\sigma'} )\!:\!S, \heap, (\CAR~x), \cred{\sigma}$  $
  \rightsquigarrow $ \\ $\rho', S, \heap[\ell := v], e, \cred{\sigma'}$}      &
{\sc car-select} \\
\hline
\makecell[t]{ $\heap(\rho(x))
\mbox{ is } \langle s, \rho'\rangle$ }& \makecell[t]{$\rho, S,
  \heap, (\CAR~x), \cred{\sigma} \rightsquigarrow $\\ $  \rho', (\rho, \rho(x),
  (\CAR~x), \cred{\sigma})\!:\!S, \heap, s, \cred{(\clazy \cup \acar)\sigma }$ }        &
{\sc car-clo}\\
\hline
\makecell[t]{$\heap(\rho(x)) \mbox{ is } (\langle s, \rho'\rangle, d)$} & \makecell[t]{$\rho,\, S,\,  \heap,\,
(\CAR~x), \cred{\sigma} \rightsquigarrow$ \\ $ \rho', \,(\rho, addr(\langle
s, \rho'\rangle), (\CAR~x),\cred{\sigma} )\!:\!S,\, \heap,\, s, \, \cred{\sigma}$ }     &
{\sc car-1-clo} \\
%% \hline
